\section{Future Work}

The future of this research can be expanded immensely. There are various aspects we can add to the existing work, or even alter the existing work. For altering existing work, we would like to in the future make a cleaner looking visualization. Currently, there seems to be some rigidness to the design where corners could be smoothed have a clearer indication of what places link up to where. We also feel that we can make the design more intuitive without adding additional elements. Other than visualization we would like to implement a better sentiment classifier. Just by polling more tweets and gaining information regarding new words, determining sarcasm, irony, or satire, and finding new linguistic patterns we believe we can gain a better classifier. Additionally we would also like to improve the sentiment prediction.

For supplementing this work, we have a few items which we believe we can add. This work as of now only sees the relation to temperature, but this study could be extended to be applied to precipitation, humidity, wind speed, or any other weather variables. There may be a significant correlation between rain amount and negative tweets. As we approach warmer climates we can conduct research regarding what the overall sentiment of people to rain, storms, and strong wind conditions. We also believe that we can determine if there is a better correlation of weather to other variables, possibly ones which are directly impacted by weather such as road accidents, calamities from natural disasters, or even medical episodes like the flu. Since there is no real way to determine if a person's mood is truly affected by weather we think using some other variables can provide more concrete correlation results.

This work can be expanded to other states and see if in more populous states the outcome would be more different. We also think that states which don't experience much seasonal change will have very different outcomes and not reflect any correlation between weather patterns and sentiment.
